Symmetric Peer-to-Peer Applications

### 2022-10-31 final/p2p-22.tex
...

We now discuss related work on time machines.
%
Regarding decentralized solutions, Fusion~\cite{fusion} is a state
synchronization networking library for the Unity game engine.
It provides networked tick-based simulation in two modes: client-server
(\emph{hosted mode}) and peer-to-peer (\emph{shared mode}).
The hosted mode is based on continuous memory snapshots, which allows for
full rollbacks when clients diverge.
However, the shared mode is less powerful and only supports eventual
consistency among clients.
We presume that continuous memory snapshots would be too costly without a
central server.
%
Regarding single-user local machines, the video game Braid%
\footnote{Braid: \burl{http://braid-game.com/}}
is designed on the assumption that players have unrestricted rollbacks as part
of the game mechanics.
Like Fusion, the implementation is based on continuous memory snapshots,
instead of deterministic simulation as we propose in this work.
%
Schuster~\cite{tml.js} proposes a simple API for time travelling in
event-driven JavaScript:
    \code{init()} to return an initial state;
    \code{handle(evt,mem)} to process events and modify state; and
    \code{render(mem)} to output the current state.
As we describe next, we use a similar approach by separating state mutation
from rendering~\cite{tml.alive}.

@@

Our middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \burl{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{Code: \burl{http://github.com/TODO-hidden-blind-review}}
is under 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \burl{http://youtube.com/TODO-hidden-blind-review}
        \label{fig.move}
    }
\end{figure}

>>>>

We now discuss related work on time machines.
%
Regarding decentralized solutions, Fusion~\cite{fusion} is a state
synchronization networking library for the Unity game engine.
It provides networked tick-based simulation in two modes: client-server
(\emph{hosted mode}) and peer-to-peer (\emph{shared mode}).
The hosted mode is based on continuous memory snapshots, which allows for
full rollbacks when clients diverge.
However, the shared mode is less powerful and only supports eventual
consistency among clients.
We presume that continuous memory snapshots would be too costly without a
central server.
%
Regarding single-user local machines, the video game Braid%
\footnote{Braid: \url{http://braid-game.com/}}
is designed on the assumption that players have unrestricted rollbacks as part
of the game mechanics.
Like Fusion, the implementation is based on continuous memory snapshots,
instead of deterministic simulation as we propose in this work.
%
Schuster~\cite{tml.js} proposes a simple API for time travelling in
event-driven JavaScript:
    \code{init()} to return an initial state;
    \code{handle(evt,mem)} to process events and modify state; and
    \code{render(mem)} to output the current state.
As we describe next, we use a similar approach by separating state mutation
from rendering~\cite{tml.alive}.

@@

Our middleware is written in C and relies on the library \emph{SDL}%
\footnote{SDL: \url{http://www.libsdl.org}}
to deal with the network, timers, and input events, such as mouse clicks and
key presses.
The full source code%
\footnote{Code: \url{http://github.com/TODO-hidden-blind-review}}
is under 500 lines of code.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{move}
    \caption[XXX] {
        A moving rectangle is controlled by peers connected indirectly.
        Users can press \code{↑ ↓ → ←} to change the direction of the
        rectangle or \code{SPACE} to pause the application.
        The inputs are applied simultaneously in all peers, as if they were
        mirrors of a single application.
        Video: \url{http://youtube.com/TODO-hidden-blind-review}
        \label{fig.move}
    }
\end{figure}
